### 2017-12-14 Sections/network_algorithms.tex
Latin quote stubs
Begin book structuring

\begin{table*}[!htb]
	\begin{tabular}{|c|c|c|c|}
		\hline
  		Algorithm & Description & Complexity class & Scaling \\
  		\hline
  		\hline
  		Breadth-first-search & Explore all vertices in a graph & \textbf{P} & $O(|V|+|E|)$ \\
  		\hline
  		Depth-first-search & (same as above) & \textbf{P} & $O(|V|+|E|)$ \\
		\hline
  		Shortest-path (Dijkstra) & Find the shortest route between two nodes & \textbf{P} & $O(|V|^2)$ \\
  		& in a directed graph & &  \\
  		  		\hline
		Shortest-path (\textit{A*}) & (same as above) & \textbf{P} & (varying) \\
  		  		\hline
		Single-source shortest path & Find the shortest paths from a given node to & \textbf{P} & $O(|V|\cdot |E|)$\\
  		& \textit{all} other nodes & & \\
 		\hline
Minimum spanning tree & Find a spanning tree of a graph that minimises & \textbf{P} & $O(|E|\text{log}|V|)$ \\
  		& the total of the edge weights & & \\
  		\hline
  		Minimum cost flow & Minimise total costs in a network &  \textbf{P} & $O(|V|\text{log}|V|(|E|$\\
  		(Orlin)& with a specified amount of flow& & $+|V|\text{log}|V|))$ \\
  		\hline
  		Maximum flow & Maximise flow in a network, regardless of costs & \textbf{P} & $O(|E|\cdot c_\text{max})$ \\
  		(Ford-Fulkerson) & & & \\
  		\hline
  		Multi-commodity flow & Same as maximum flow, but generalised to & \textbf{NP}-complete & ? \\
  		& arbitrary numbers of users & (exactly), & \\
  		& & \textbf{P} (approximation & \\
  		& & using heuristics) & \\
  		\hline
  		Vehicle routing problem & Generalises the shortest-path algorithm to multiple & \textbf{NP}-complete & ? \\
  		& users, with distinct sources and destinations & & \\ 
  		\hline
  		Vehicle rescheduling problem & Same as above but with dynamically changing costs & \textbf{NP}-complete & ? \\
    	\hline
	\end{tabular}
	\caption{Summary of some important network algorithms and their complexities. The \textbf{NP}-complete algorithms are not believed to have efficient classical algorithms, and their exact scaling is not well understood.} \label{tab:net_alg_sum} \index{Network algorithms}\index{Breadth-first-search algorithm}\index{Depth-first-search algorithm}\index{Shortest-path algorithm}\index{Single-source shortest path algorithm}\index{Minimum spanning tree algorithm}\index{Minimum cost flow algorithm}\index{Maximum flow algorithm}\index{Multi-commodity flow algorithm}\index{Vehicle routing problem}\index{Vehicle rescheduling problem}
\end{table*}

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function DijkstraShortestPath($G$,$A$,$B$):
\begin{enumerate}
	\item currentNode = $A$
    \item tentativeDistances[$A$] = 0
    \item tentativeDistances[others] = $\infty$
    \item nodesVisited[$A$] = True
    \item nodesVisited[others] = False
    \item loopStart:
    \item neighbours = currentNode.neighbourhood
    \item nodesVisited[neighbours] = True
    \item for(n$\in$neighbours) \{
    \setlength{\itemindent}{0.2in}
    \item newTentativeDist = \\ min(tentativeDistances[currentNode] \\+ edgeWeight[currentNode,n],\\
        tentativeDistances[n])\\
    \item nodesVisited[currentNode] = True
    \setlength{\itemindent}{0in}
    \item \}
    \item if(nodesVisited[$B$] = True) \{
    \setlength{\itemindent}{0.2in}
	\item return(tentativeDistances[$B$])
	\item $\Box$
    \setlength{\itemindent}{0in}
    \item \}
	\item currentNode = \\
	tentativeDistances[unvisitedNodes].\\
	nodeWithSmallest()
	\item goto(loop)
    \item $\Box$
\end{enumerate}}}}
\caption{Dijkstra's original shortest-path algorithm for finding the lowest weight path through a graph, $G$, between two vertices, $A$ (source) and $B$ (destination). The algorithm has $O(|V|^2)$ runtime (in \textbf{P}). \comment{Fix me}} \label{alg:dijkstra}\index{Shortest-path algorithm}
\end{table}

>>>>

\begin{table*}[!htb]
	\begin{tabular}{|c|c|c|c|}
		\hline
  		Algorithm & Description & Complexity class & Scaling \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Breadth-first-search & Explore all vertices in a graph & \textbf{P} & $O(|V|+|E|)$ \\
  		\hline
  		\rowcolor{LimeGreen} Depth-first-search & (same as above) & \textbf{P} & $O(|V|+|E|)$ \\
		\hline
  		\rowcolor{LimeGreen} Shortest-path (Dijkstra) & Find the shortest route between two nodes & \textbf{P} & $O(|V|^2)$ \\
  		\rowcolor{LimeGreen} & in a directed graph & &  \\
  		  		\hline
		\rowcolor{LimeGreen} Shortest-path (\textit{A*}) & (same as above) & \textbf{P} & (varying) \\
  		  		\hline
		\rowcolor{LimeGreen} Single-source shortest path & Find the shortest paths from a given node to & \textbf{P} & $O(|V|\cdot |E|)$\\
  		\rowcolor{LimeGreen} & \textit{all} other nodes & & \\
 		\hline
\rowcolor{LimeGreen} Minimum spanning tree & Find a spanning tree of a graph that minimises & \textbf{P} & $O(|E|\text{log}|V|)$ \\
  		\rowcolor{LimeGreen} & the total of the edge weights & & \\
  		\hline
  		\rowcolor{LimeGreen} Minimum cost flow & Minimise total costs in a network &  \textbf{P} & $O(|V|\text{log}|V|(|E|$\\
  		\rowcolor{LimeGreen} (Orlin)& with a specified amount of flow& & $+|V|\text{log}|V|))$ \\
  		\hline
  		\rowcolor{LimeGreen} Maximum flow & Maximise flow in a network, regardless of costs & \textbf{P} & $O(|E|\cdot c_\text{max})$ \\
  		\rowcolor{LimeGreen} (Ford-Fulkerson) & & & \\
  		\hline
  		\rowcolor{Lavender} Multi-commodity flow & Same as maximum flow, but generalised to & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & arbitrary numbers of users & (exactly), & \\
  		\rowcolor{Lavender} & & \textbf{P} (approximation & \\
  		\rowcolor{Lavender} & & using heuristics) & \\
  		\hline
  		\rowcolor{Lavender} Vehicle routing problem & Generalises the shortest-path algorithm to multiple & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & users, with distinct sources and destinations & & \\ 
  		\hline
  		\rowcolor{Lavender} Vehicle rescheduling problem & Same as above but with dynamically changing costs & \textbf{NP}-complete & ? \\
    	\hline
	\end{tabular}
	\caption{Summary of some important network algorithms and their complexities. The \textbf{NP}-complete algorithms are not believed to have efficient classical algorithms, and their exact scaling is not well understood.} \label{tab:net_alg_sum} \index{Network algorithms}\index{Breadth-first-search algorithm}\index{Depth-first-search algorithm}\index{Shortest-path algorithm}\index{Single-source shortest path algorithm}\index{Minimum spanning tree algorithm}\index{Minimum cost flow algorithm}\index{Maximum flow algorithm}\index{Multi-commodity flow algorithm}\index{Vehicle routing problem}\index{Vehicle rescheduling problem}
\end{table*}

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function DijkstraShortestPath($G$,$A$,$B$):
\begin{enumerate}
	\item currentNode = $A$
    \item tentativeDistances[$A$] = 0
    \item tentativeDistances[others] = $\infty$
    \item nodesVisited[$A$] = True
    \item nodesVisited[others] = False
    \item loopStart:
    \item neighbours = currentNode.neighbourhood
    \item nodesVisited[neighbours] = True
    \item for(n$\in$neighbours) \{
    \setlength{\itemindent}{0.2in}
    \item newTentativeDist = \\ min(tentativeDistances[currentNode] \\+ edgeWeight[currentNode,n],\\
        tentativeDistances[n])\\
    \item nodesVisited[currentNode] = True
    \setlength{\itemindent}{0in}
    \item \}
    \item if(nodesVisited[$B$] = True) \{
    \setlength{\itemindent}{0.2in}
	\item return(tentativeDistances[$B$])
	\item $\Box$
    \setlength{\itemindent}{0in}
    \item \}
	\item currentNode = \\
	tentativeDistances[unvisitedNodes].\\
	nodeWithSmallest()
	\item goto(loopStart)
    \item $\Box$
\end{enumerate}}}}
\caption{Dijkstra's original shortest-path algorithm for finding the lowest weight path through a graph, $G$, between two vertices, $A$ (source) and $B$ (destination). The algorithm has $O(|V|^2)$ runtime (in \textbf{P}). \comment{Fix me}} \label{alg:dijkstra}\index{Shortest-path algorithm}
\end{table}

### 2017-12-14 Sections/optical_stability_in_quantum_networks.tex
Latin quote stubs
Begin book structuring

\begin{figure}[!htb]
	\includegraphics[width=\columnwidth]{wavepacket} \\
	\caption{(top) A photonic wave-packet of the form of Eq.~(\ref{eq:wavepacket_modulated}), with Gaussian temporal envelope of width $\sigma$ (orange), shifted by a carrier frequency $\omega_0$ (blue).} \label{fig:HOM_vs_MZ}
\end{figure}

@@

\begin{figure}[!htb]
	\includegraphics[width=\columnwidth]{MZ_setup} \\
	\includegraphics[width=\columnwidth]{MZ}
	\caption{Mach-Zehnder self-interference of a single photon. (top) Layout of the interferometer. The photon is subject to a time-delay $\tau$ within only the upper arm of a balanced interferometer, comprising two 50:50 beamsplitters. (bottom) Interference fringe $P_\text{MZ}(\tau)$ as a function of the time-delay. The interference is sensitive at the scale of the photon wavelength, (blue) in Fig.~\ref{fig:HOM_vs_MZ}.} \label{fig:MZ_inter}
\end{figure}

@@

\begin{figure}[!htb]
	\includegraphics[width=0.63\columnwidth]{HOM_setup} \\
	\includegraphics[width=\columnwidth]{HOM}
	\caption{Hong-Ou-Mandel interference between two independent photons, $A$ and $B$. (top) Layout of the interferometer. Two photons given by mode operators $\hat{A}^\dag$ and $\hat{B}^\dag$\index{Mode operators} (Sec.~\ref{sec:spatio_temporal}), both with temporal distribution function $\psi(t)$, interfere at a 50:50 beamsplitter, where mode $A$ is first subject to a time-delay $\tau$. (bottom) Interference fringe $P_\text{HOM}(\tau)$ as a function of the time-delay. The fringe is only sensitive at the scale of the wave-packet envelope, (orange) in Fig.~\ref{fig:HOM_vs_MZ}.} \label{fig:HOM_inter}
\end{figure}

@@

\begin{table}[!htb]
	\begin{tabular}{|c|c|}
		\hline
  		Protocol & Interference type \\
  		\hline
  		\hline
  		Cluster state measurement & None \\
   		Quantum anonymous broadcasting & None \\
  		QKD (BB84, E91) & None \\
  		Quantum memory & None \\
  		Quantum process tomography & None \\
  		Quantum state tomography & None \\
  		Random number generation & None \\
  		Separable measurements & None \\
  		Separable state preparation & None \\
  		Optical interfacing & None \\
  		\hline
  		Cluster state preparation (fusion gates) & HOM \\
  		Entanglement purification & HOM \\
  		Entanglement swapping & HOM \\ 
  		Matter qubit entangling operations & HOM \\
  		Partial Bell state measurements & HOM \\
   		Quantum gate teleportation & HOM \\
  		Quantum state teleportation & HOM \\
  		Superdense coding & HOM \\
  		\hline
  		{\sc BosonSampling} & MZ \\
  		General linear optics networks & MZ \\
  		Universal LOQC (KLM) & MZ \\
  		Quantum metrology & MZ \\
  		Quantum walks & MZ \\
    	\hline
	\end{tabular}
	\caption{Summary of the major quantum network protocols presented in Sec.~\ref{sec:protocols_quant_int}, and their required type of interference.}\index{Interferometric requirements}\label{table:summary_inter}
\end{table}

>>>>

\begin{figure}[!htb]
	\includegraphics[width=0.47\textwidth]{wavepacket} \\
	\caption{(top) A photonic wave-packet of the form of Eq.~(\ref{eq:wavepacket_modulated}), with Gaussian temporal envelope of width $\sigma$ (orange), shifted by a carrier frequency $\omega_0$ (blue).} \label{fig:HOM_vs_MZ}
\end{figure}

@@

\begin{figure}[!htb]
	\includegraphics[width=0.47\textwidth]{MZ_setup} \\
	\includegraphics[width=0.47\textwidth]{MZ}
	\caption{Mach-Zehnder self-interference of a single photon. (top) Layout of the interferometer. The photon is subject to a time-delay $\tau$ within only the upper arm of a balanced interferometer, comprising two 50:50 beamsplitters. (bottom) Interference fringe $P_\text{MZ}(\tau)$ as a function of the time-delay. The interference is sensitive at the scale of the photon wavelength, (blue) in Fig.~\ref{fig:HOM_vs_MZ}.} \label{fig:MZ_inter}
\end{figure}

@@

\begin{figure}[!htb]
	\includegraphics[width=0.325\textwidth]{HOM_setup} \\
	\includegraphics[width=0.47\textwidth]{HOM}
	\caption{Hong-Ou-Mandel interference between two independent photons, $A$ and $B$. (top) Layout of the interferometer. Two photons given by mode operators $\hat{A}^\dag$ and $\hat{B}^\dag$\index{Mode operators} (Sec.~\ref{sec:spatio_temporal}), both with temporal distribution function $\psi(t)$, interfere at a 50:50 beamsplitter, where mode $A$ is first subject to a time-delay $\tau$. (bottom) Interference fringe $P_\text{HOM}(\tau)$ as a function of the time-delay. The fringe is only sensitive at the scale of the wave-packet envelope, (orange) in Fig.~\ref{fig:HOM_vs_MZ}.} \label{fig:HOM_inter}
\end{figure}

@@

\begin{table}[!htb]
	\begin{tabular}{|c|c|}
		\hline
  		Protocol & Interference type \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Cluster state measurement & None \\
   		\rowcolor{LimeGreen} Quantum anonymous broadcasting & None \\
  		\rowcolor{LimeGreen} QKD (BB84, E91) & None \\
  		\rowcolor{LimeGreen} Quantum memory & None \\
  		\rowcolor{LimeGreen} Quantum process tomography & None \\
  		\rowcolor{LimeGreen} Quantum state tomography & None \\
  		\rowcolor{LimeGreen} Random number generation & None \\
  		\rowcolor{LimeGreen} Separable measurements & None \\
  		\rowcolor{LimeGreen} Separable state preparation & None \\
  		\rowcolor{LimeGreen} Optical interfacing & None \\
  		\hline
  		\rowcolor{GreenYellow} Cluster state preparation (fusion gates) & HOM \\
  		\rowcolor{GreenYellow} Entanglement purification & HOM \\
  		\rowcolor{GreenYellow} Entanglement swapping & HOM \\ 
  		\rowcolor{GreenYellow} Matter qubit entangling operations & HOM \\
  		\rowcolor{GreenYellow} Partial Bell state measurements & HOM \\
   		\rowcolor{GreenYellow} Quantum gate teleportation & HOM \\
  		\rowcolor{GreenYellow} Quantum state teleportation & HOM \\
  		\rowcolor{GreenYellow} Superdense coding & HOM \\
  		\hline
  		\rowcolor{Lavender} {\sc BosonSampling} & MZ \\
  		\rowcolor{Lavender} General linear optics networks & MZ \\
  		\rowcolor{Lavender} Universal LOQC (KLM) & MZ \\
  		\rowcolor{Lavender} Quantum metrology & MZ \\
  		\rowcolor{Lavender} Quantum walks & MZ \\
    	\hline
	\end{tabular}
	\caption{Summary of the major quantum network protocols presented in Sec.~\ref{sec:protocols_quant_int}, and their required type of interference.}\index{Interferometric requirements}\label{table:summary_inter}
\end{table}
